\chapter{Introduction}
\labch{intro}
	\section{Purpose}
		During their university studies, in order to start entering the workforce, a student might decide to apply for an internship related to their field of study. Similarly, companies offering internships may be interested in finding students that are adequate for them. To facilitate the matching between students and companies, a new platform called \emph{Students and Companies} (S\&C) is to be developed. S\&C allows companies to look for suitable students by publish internship advice on the platform, while students can look for internships that interest them. Moreover, the platform implements recommendation mechanism to help student and companies to find each other. Once the contact is established, S\&C can provide support to the students selection process.
	\section{Scope}
		As mentioned in the RASD document, there are two main users categories that interact with the system: \emph{Companies} and \emph{Students}. The companies publish announcements about the internships they want to offer where they specify \emph{projects} that will be carried out and the \emph{terms} of the offer. The system itself informs the companies about the availability of students who may be suitable for their internships (based on their profile).
		
		Students, on the other hand, may use the platform to look for internships and S\&D can also notify them if there are new internships that could meet their interests, but they can still independently search through all the available internships.
		
		Once a \emph{contact} is established and accepted by the two parties, the student selection process begins. At this point the company defines selection steps and schedules the interviews for each student. Once the selection is over, the system collects feedback and suggestions from both students and companies.
		
		Finally, both students and companies can monitor the progress of the internships by providing information on its development and any issues that may arise.
		
	\section{Definitions, Acronyms and Abbreviations}
		\subsection{Definitions}
			\begin{itemize}
				\item \textbf{internship advice} : a call for application related to an internship that will be offered by a company;
				\item \textbf{recommendation} : the mechanism related to the fact that the system both informs students whether new internship advice that might interest them are published and notifies companies of the presence of students that might be suitable for their internships;
				\item \textbf{project} (of an internship advice) : the definition of the application domain, the set of tasks to be performed and the set of the most relevant adopted technologies (if any) for an internship;
				\item \textbf{terms} (of an internship advice) : the set of benefits offered by an internship (e.g. paid/not paid, training, lunch voucher... );
				\item \textbf{selection process} : each internship advice is followed by a sequence of selection steps.
			\end{itemize}
		\subsection{Acronyms}
			\begin{itemize}
				\item S\&C: Students\&Companies, the name of the platform;
				\item UML: Unified Modeling Language;
				\item CV: Curriculum Vitae.
				\item DB: Database
				\item RDBMS: Relational Database Management System
				\item API: Application Programming Interface
			\end{itemize}
		\subsection{Abbreviations}
			\begin{itemize}
				\item Gn: Goal number n;
				\item Rn: Requirement number n;
				\item Dn: Domain assumption number n;
				\item WPn: World Phenomena number n;
				\item SPn: Shared Phenomena number n;
				\item UC: Use Case.
				\item UI: User Interface
			\end{itemize}
	\section{Revision history}
		\begin{center}
			\begin{tikzpicture}
				% draw a horizontal line
				\draw (0,0) -- (12,0);
				
				% draw vertical lines
				\foreach \x in {1}
				\draw (\x cm,3pt) -- (\x cm,-3pt);
				
				% draw nodes to add events
				\draw (1,0) node[below=3pt] {22/12/2024} node[above=3pt] {First version};
			\end{tikzpicture}
		\end{center}
	\section{Reference documents}
		The Documents used to deliver the RASD document are the following:
		\begin{itemize}
			\item the Specification of RASD and DD assignment of Software Engineering 2;
			\item the class slides on WeBeep, in particular slides on UML diagrams, software architectures styles and the part related to Integration and Testing
		\end{itemize}
	\section{Document structure}
		\begin{enumerate}
			\item \textbf{Introduction}: this section provides a brief introduction to the purpose of the platform to be developed, S\&C in this case, focusing in particular on the most important goals which the system has to achieve and on the various phenomena identified, as we mentioned in the RASD document;
			\item \textbf{Architectural Design} : this section provide a description on the general architecture chosen for the system, at different levels of granularity: it focuses on the component of the architecture, on how they are related (showing also how the most important functionalities of the platform are provided) and on the deployment view;
			\item \textbf{User Interface Design} : in this section it is explained how the User Interface is designed to provide the functionalities of the platform
			\item \textbf{Requirement Traceability} : in this section is explained how the goals described in the RASD document are satisfied showing the interaction between the requirements and the components of the architecture;
			\item \textbf{Implementation, Integration and Test Plan}: this section provides a description of how the components of the system are integrated and then tested; this information are useful for the developers of the platform
			\item \textbf{Effort Spent}:report of the time spent by any group member in any document section;
			\item \textbf{References}: list of software and documents used to develop the document.
		\end{enumerate}